---
title: "williamdavis"
author: "William Davis"
date: "4/10/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Create a dataframe of your bag including the following
  - Name of each club
  - Average distance for each shot


```{r Create Bag}
club <- c("driver", "3 wood", "5 wood", "4 iron", "5 iron", "6 iron", "7 iron", "8 iron",
          "9 iron", "P Wedge", "50 Degree", "54 Degree", "58 Degree")
distance <- c(260, 220, 200, 185, 175, 165, 150, 135, 125, 115, 100, 85, 70)

bag <-create.bag(club, distance)

```

## Create a handicap
  - The handicap system gives players a measurment for how well they should be scoring
  - The system is on a rating of 0-36 with better players having lower numbers
    - Going below 0 is possible but is only for extremly talented golfers
    - This number would then be considered to be a +(Handicap)
  - Your handicap is the rating at which youve played the last 10 Games
 

```{r Generate Handicap}
scores <- c(10, 12, 8, 9, 9, 10, 8, 9, 8, 9)

handicap <- set.handicap(scores)


```

## Course handicap and target score
  - Each course is given a rating and a slope to the par for the course
  - Rating is how well a scractch golfer should play
    - Scratch is 0 handicap
    - Easier courses have a lower rating and a harder courses have a higher rating
  - Slope is how well a bogey gofler should should play
    - This is a rating for how condtions may affect higher handicap players
    - A bogey golfer is someone who is averaging around one stroke over par per hole
    - Same characteristics of difficulty for Rating apply to Slope
  - A course handicap takes into account the difficulty of the course and your handicap
  - The course handicap plus par is the target score for the round
    


```{r Generate Course Handicap}
#For this example, the we know the handicap index, slope rating, course rating and par.
# these are randomly generated but are realistic numbers

course <- course.handicap(handicap, 120, 73.2, 72)

target <- set.targetscore(72, course)

```

## Club to hit and target
  - There are many factors that go into hitting each type of shot (Wind, shot shape, hazards)
  - Ideally the golfer should know distance to hazards are 
  - They should also know what shot shape they are going to hit
    - Experienced golfers can choose their shot shape with practice
      - Fade: starts straight and funnels right towards end
      - Draw: starts stright and funnels left at end
    - Most amateur golfer will hit one type of shot shape without intention
  - Wind coupled with trajectory will affect how far the ball will travel both in distance and laterally 



```{r}

shot(bag, 135)

```

